---
output:
  pagedown::html_paged:
    number_sections: false
    css: ["academic_cv.css"]
links-to-footnotes: true
knit: pagedown::chrome_print
---

<style>
:root{
  --last-updated: "\00a0 \00a0 \00a0 \00a0 Last updated: `r format(Sys.Date(), '%B, %Y')`";
}
</style>

```{r setup, include=FALSE}
# devtools::install_github("ulyngs/pagedownCV@764efda91fef9b6ef22e5df2f4979a1e1a836ee0")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
library(pagedownCV)

# read in CV data from e.g. an Excel spreadsheet --- the sample CV data is from this google sheet https://docs.google.com/spreadsheets/d/1ta71CAGkcLqm-W1UdVRA_JJSddWV2TsrRZsCnQlmOis/edit?usp=sharing
cv_entries <- read_excel("cv_wsx.xlsx", sheet = "cv_entries")
publications <- read_excel("cv_wsx.xlsx", sheet = "publications")

```

::: {.title-and-contact}

:::::: {.title}
<h1 class="title">Shixiang Wang <br>王诗翔</h1>
::::::

:::::: {.contact-info}
wangsx1@sysucc.org.cn  \
<u><a href="https://github.com/ShixiangWang">github.com/ShixiangWang</a></u> \
<u><a href="https://orcid.org/0000-0001-9855-7357">ORCID</a></u>
<u><a href="https://scholar.google.com/citations?hl=en&user=FvNp0NkAAAAJ">Scholar</a></u>
::::::

:::

## Research summary
::: {.research-interests}

:::::: {.spacer}
::::::

:::::: {.interests}
I am a computational biologist working on cancer genomics. I use bioinformatics skills to decode the unfound patterns
in cancer, and explore biomarkers for explaining the cancer heterogeneity and predicting the efficacy of cancer treatments, mainly in immunotherapy.

**I am passionate about** open science and developing open-source analysis toolkits. Because of this,
currently I am a community member of [Openbiox](https://github.com/openbiox), [rOpenSci](https://ropensci.org/) and [Bioconductor](https://www.bioconductor.org/). My long-term goal in academic field is being a master in a
subfield of cancer bioinformatics and trying my best to continually boost the open-source bioinformatics ecosystem in China.
::::::
:::

::: {.cv-entries}
## Research positions
```{r}
cv_entries |>  
  filter(type == 'research_positions', is.na(exclude)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```



## Education
```{r}
cv_entries |> 
  filter(type == 'education') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```

## Major grants and funding
```{r}
cv_entries |>
  filter(type == 'major_grants') |>
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br>{additional_info}"))) |>
  select(year, what) |>
  kable()
```

## Awards & honours
```{r}
cv_entries |> 
  filter(type == 'awards') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>  
  blank_year_when_repeated() |> 
  select(year, what) |> 
  kable()
```


## Publications {.three-split}

<h3>Journal articles <span class="review-note">(fully reviewed, † for co-first, \* for corresponding)</span></h3>

```{r}
publications_formatted <- publications |> 
  mutate(authors = map_chr(authors, replace_first_names_in_author_list_with_initial_and_dot), # e.g. U. Lyngs instead of Ulrik Lyngs
         authors = str_replace(authors, "U\\. Lyngs", "*U\\. Lyngs*"))    # make my name italic
```


```{r}
publications_formatted |>
  filter(type == "journal article") |> 
  mutate(venue = if_else(!mark %in% c(NA, ""), glue("{venue} <b>({mark})</b>"), venue, venue)) |> 
  mutate(venue = if_else(!is.na(url), glue("<a href='{url}'>{venue}</a>"), venue)) |> 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue}</span>")) |> 
  add_leading_zeroes_and_letter("J") |> 
  blank_year_when_repeated() |>
  select(year, number, citation) |>
  manual_page_break_after_row("citation", "CDC20") |> 
  kable(longtable=TRUE)
```

> The journal impact factors mentioned above are derived from the maximum values in the history of journal impact factors. Journal impact factors, Chinese Academy of Sciences (CAS) categorization, and JCR categorization were all uniformly updated on 2023.11.02. For future publications that are included, I will update them selectively and will no longer perform uniform updates on all publications.

<br class="pageBreak">

<h3>Preprints<span class="review-note"> (not reviewed, † for co-first, \* for corresponding)</span></h3>

```{r}
publications_formatted |>
  filter(type == "preprint") |> 
  # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honourable") ~ glue("<br>", fa("award"), " <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br>", fa("trophy"), " <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) |>
  # create citations
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue}</span>{award}")) |> 
  # number entries with a prefix
  add_leading_zeroes_and_letter("P") |> 
  blank_year_when_repeated() |> 
  select(year, number, citation) |>
  knitr::kable()
```


## Cited by

```{r fig.width=7, fig.height=3}
# Code written by Guangchuang Yu, modified by Shixiang
library(ggplot2)
library(tinyscholar)
library(ggstance)
library(ggtree)
library(ggimage)

id <- 'FvNp0NkAAAAJ'

citation <- tinyscholar::tinyscholar(id)$citation
total_citation <- citation[[2]][1]
citation <- citation[-1, ] # remove 'total' row
names(citation) <- c("year", "cites")
citation$year <- as.numeric(citation$year)

citation$year <- factor(citation$year)

p <- ggplot(citation, aes(cites, year)) +
  geom_barh(stat = "identity", fill = "#96B56C") +
  geom_text2(aes(label = cites, subset = cites > max(cites) / 5), hjust = 1.1, size = 5) +
  labs(caption = glue("Total citations: {total_citation}; Source: Google Scholar")) +
  scale_x_continuous(position = "top") +
  theme_minimal(base_size = 14) +
  xlab(NULL) +
  ylab(NULL) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(linetype = "dashed"),
    plot.caption = element_text(colour = "grey30")
  ) +
  theme_transparent()

p
```


## Talks {.three-split}


```{r}
cv_entries |> 
  filter(type == 'talk', is.na(exclude)) |> 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), as.character(department)),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) |>
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) |> 
  add_leading_zeroes_and_letter("T") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |> 
  knitr::kable()

```



## Poster presentations {.three-split}
```{r}
cv_entries |> 
  filter(type == 'poster') |>
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), as.character(department))) |>
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) |> 
  add_leading_zeroes_and_letter("P") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |>
  knitr::kable()

```

## Teaching experience
```{r}
cv_entries |> 
  filter(type == 'teaching') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
         "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```

## Service
```{r}
cv_entries |> 
  filter(type == 'service') |> 
  mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) |>
  arrange(desc(date_end), desc(date)) |> 
  select(year, what) |> 
  kable()
```


<!-- <br class="pageBreak"> -->








:::

<!-- <br class="pageBreak"> -->

# Links
