---
output:
  pagedown::html_paged:
    number_sections: false
    css: ["academic_cv.css"]
links-to-footnotes: true
knit: pagedown::chrome_print
---

<style>
:root{
  --last-updated: "\00a0 \00a0 \00a0 \00a0 Last updated: `r format(Sys.Date(), '%B, %Y')`";
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(glue)
library(fontawesome)
library(readxl)
library(pagedownCV)

# read in CV data from e.g. an Excel spreadsheet --- the sample CV data is from this google sheet https://docs.google.com/spreadsheets/d/1ta71CAGkcLqm-W1UdVRA_JJSddWV2TsrRZsCnQlmOis/edit?usp=sharing
cv_entries <- read_excel("cv_wsx.xlsx", sheet = "cv_entries")
publications <- read_excel("cv_wsx.xlsx", sheet = "publications")

```

::: {.title-and-contact}

:::::: {.title}
<h1 class="title">Shixiang Wang <br>王诗翔</h1>
::::::

:::::: {.contact-info}
wangsx1@sysucc.org.cn  \
<u><a href="https://github.com/ShixiangWang">github.com/ShixiangWang</a></u>
::::::

:::

## Research summary
::: {.research-interests}

:::::: {.spacer}
::::::

:::::: {.interests}
**Aims---**to develop and evaluate design patterns that help people self-regulate their use of smartphones and laptops.
<br>
**Methods---**controlled studies, user surveys, interviews, co-design workshops, web scraping, behaviour logging.

**I am passionate about** open and transparent research. 
Since 2018, I have shared materials, analysis scripts, and data for all my first-authored work, and written my papers as reproducible documents in [R Markdown](https://rmarkdown.rstudio.com).
::::::
:::

::: {.cv-entries}
## Research positions
```{r}
cv_entries |>  
  filter(type == 'research_positions', is.na(exclude)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```



## Education
```{r}
cv_entries |> 
  filter(type == 'education') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```

## Major grants and funding
```{r}
cv_entries |>
  filter(type == 'major_grants') |>
  mutate(what = if_else(is.na(additional_info),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
                        glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br>{additional_info}"))) |>
  select(year, what) |>
  kable()
```

## Awards & honours
```{r}
cv_entries |> 
  filter(type == 'awards') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) |>  
  blank_year_when_repeated() |> 
  select(year, what) |> 
  kable()
```


## Publications {.three-split}

:::::: {.grid-container-publications}
<h3>Journal articles <span class="review-note">(fully reviewed)</span></h3>
::::::

```{r}
publications_formatted <- publications |> 
  mutate(authors = map_chr(authors, replace_first_names_in_author_list_with_initial_and_dot), # e.g. U. Lyngs instead of Ulrik Lyngs
         authors = str_replace(authors, "U\\. Lyngs", "*U\\. Lyngs*"))    # make my name italic
```


```{r}
publications_formatted |>
  filter(type == "journal article") |> 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue}</span>")) |> 
  add_leading_zeroes_and_letter("J") |> 
  blank_year_when_repeated() |>
  select(year, number, citation) |>
  manual_page_break_after_row("citation", "Sigflow") |> 
  kable(longtable=TRUE)
```



:::::: {.grid-container-publications}
<h3>Preprints<span class="review-note"> (not reviewed)</span></h3>
::::::

```{r}
publications_formatted |>
  filter(type == "preprint") |> 
  # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honourable") ~ glue("<br>", fa("award"), " <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br>", fa("trophy"), " <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) |>
  # create citations
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors}</span><br>",
                         "<span class='publication-venue'>{venue}</span>{award}")) |> 
  # number entries with a prefix
  add_leading_zeroes_and_letter("P") |> 
  blank_year_when_repeated() |> 
  select(year, number, citation) |>
  knitr::kable()
```

## Talks {.three-split}


```{r}
cv_entries |> 
  filter(type == 'talk', is.na(exclude)) |> 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), as.character(department)),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) |>
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) |> 
  add_leading_zeroes_and_letter("T") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |> 
  manual_page_break_after_row("what", "Studying the Digital Backlash") |> 
  manual_page_break_after_row("what", "OxDEG") |> 
  manual_page_break_after_row("what", "Culturally Evolved Tool") |> 
  knitr::kable()

```



## Poster presentations {.three-split}
```{r}
cv_entries |> 
  filter(type == 'poster') |>
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), as.character(department))) |>
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) |> 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) |> 
  add_leading_zeroes_and_letter("P") |> 
  blank_year_when_repeated() |> 
  select(year, number, what) |>
  knitr::kable()

```


## Teaching experience
```{r}
cv_entries |> 
  filter(type == 'teaching') |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>",
         "{additional_info}")) |> 
  select(year, what) |> 
  kable()
```

<!-- <br class="pageBreak"> -->


## Service
```{r}
cv_entries |> 
  filter(type == 'service') |> 
  mutate(where = if_else(!is.na(url), glue("[{where}]({url})"), where)) |> 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span> {where}")) |>
  arrange(desc(date_end), desc(date)) |> 
  select(year, what) |> 
  kable()
```


<!-- <br class="pageBreak"> -->








:::

<!-- <br class="pageBreak"> -->

# Links
